---
title: "Behavior Minimization"
author: "Mariano Cerrutti"
date: "5/26/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      results= "asis")
#install.packages("dplyr")
#install.packages("magrittr")
#install.packages("ggplot2")
#install.packages("jsonlite")
install.packages("xtable")
library(dplyr)
library(magrittr)
library(ggplot2)
library(jsonlite)
library(gridExtra)
library(grid)
library(lattice)
library(knitr)
library(scales)
library(xtable)
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
experimental_composite <- read.csv(file='/home/mariano/code/henos-automata/doc/experimental_setting/tmp_results/unrealizable_data_composite.csv')
experimental_composite$liveness_count <- experimental_composite$guarantees_count + experimental_composite$assumptions_count
experimental_composite$reduction <- experimental_composite$minimization_transitions / experimental_composite$plant_transitions
summ_unreal <- experimental_composite %>%
  group_by(name) %>%
  summarize(diag = mean(diagnosis_time), liveness = max(liveness_count), plant_trans = max(plant_transitions),
            min_trans = max(minimization_transitions), red = mean(reduction), steps = max(diagnosis_steps))
realizable_composite = read.csv(file='/home/mariano/code/henos-automata/doc/experimental_setting/tmp_results/realizable_data_composite.csv')
summ_real <- realizable_composite %>%
  group_by(name) %>%
  summarize(plant_states = max(plant_states), plant_trans = max(plant_transitions),  plant_trans = max(plant_transitions),  min_trans = max(minimization_transitions))

genbuf_missing <- subset(summ_unreal, grepl("Genbuf\\.\\d\\.\\(missing", name))
genbuf_removed <- subset(summ_unreal, grepl("Genbuf\\.\\d\\.\\(removed", name))
collector_missing <- subset(summ_unreal, grepl("Collector\\.\\d\\.\\(missing", name))
robot_missing <- subset(summ_unreal, grepl("Robot", name) & grepl("missing", name))
robot_removed <- subset(summ_unreal, grepl("Robot", name) & grepl("removed", name))

genbuf_real <- subset(summ_real, grepl("Genbuf", name))
genbuf_real_b <- genbuf_real[1:(nrow(genbuf_real)-1),]
collector_real <- subset(summ_real, grepl("Collector", name))
robot_real <- subset(summ_real, grepl("Robot", name))

genbuf_missing$reduction_ctrl <- genbuf_missing$plant_trans / genbuf_real$plant_trans
genbuf_missing$ctrl_states <- genbuf_real$plant_states
genbuf_missing$ctrl_transitions <- genbuf_real$plant_trans
genbuf_removed$reduction_ctrl <- genbuf_removed$plant_trans / genbuf_real_b$plant_trans
genbuf_removed$ctrl_states <- genbuf_real_b$plant_states
genbuf_removed$ctrl_transitions <- genbuf_real_b$plant_trans
collector_missing$reduction_ctrl <- collector_missing$plant_trans / collector_real$plant_trans
collector_missing$ctrl_states <- collector_real$plant_states
collector_missing$ctrl_transitions <- collector_real$plant_trans
robot_missing$reduction_ctrl <- robot_missing$plant_trans / robot_real$plant_trans
robot_missing$ctrl_states <- robot_real$plant_states
robot_missing$ctrl_transitions <- robot_real$plant_trans
robot_removed$reduction_ctrl <- robot_removed$plant_trans / robot_real$plant_trans
robot_removed$ctrl_states <- robot_real$plant_states
robot_removed$ctrl_transitions <- robot_real$plant_trans

composite_table <- rbind(collector_missing, robot_missing, robot_removed, genbuf_missing, genbuf_removed)

print(xtable(composite_table, type = "latex"), file = "/home/mariano/code/henos-automata/doc/experimental_setting/tmp_results/experimental_data.tex")

```
<style type="text/css">
.twoC {width: 100%}
.clearer {clear: both}
.twoC .table {max-width: 50%; float: right}
.twoC img {max-width: 50%; float: left}
table {
  margin: auto;
  border-top: 1px solid #666;
  border-bottom: 1px solid #666;
}
table thead th { border-bottom: 1px solid #ddd; }
th, td { padding: 5px; }
thead, tfoot, tr:nth-child(even) { background: #eee; }
pre{display:none;}
</style>

# Selected Graphs

## General Table

Specification sizes go from `r min(experimental_composite$plant_transitions)` transitions up to `r max(experimental_composite$plant_transitions)`.
Minimization reduction goes from `r max(experimental_composite$minimization_transitions / experimental_composite$plant_transitions)` up to `r min(experimental_composite$minimization_transitions / experimental_composite$plant_transitions)`.

```{r echo=FALSE}
times_table <- experimental_composite[c(1,7)]
times_table$liveness_count <- experimental_composite$guarantees_count + experimental_composite$assumptions_count
times_table$plant_transitions <- experimental_composite$plant_transitions
times_table$minimization_transitions <- experimental_composite$minimization_transitions
times_table$reduction <- experimental_composite$minimization_transitions / experimental_composite$plant_transitions
times_table$steps <- experimental_composite$diagnosis_steps
times_table <- times_table %>%
  group_by(name) %>%
  summarize(diag <- mean(diagnosis_time), liveness <- max(liveness_count), plant_trans <- max(plant_transitions),
            min_trans <- max(minimization_transitions), red <- mean(reduction), steps <- max(steps))
kable(times_table, caption = "Times table", col.names=c("Specification","Diagnosis(s)","Liveness fluents", "Plant transitions", "Min. transitions","Minimization pct.(%)","Min. steps"))
```

## Minimization distribution (overall)

```{r echo=FALSE}
experimental_composite$m_coeff = experimental_composite$minimization_transitions / experimental_composite$plant_transitions
experimental_composite$relative_time = experimental_composite$diagnosis_time / experimental_composite$plant_transitions
experimental_composite$relative_time_liveness = experimental_composite$diagnosis_time / (experimental_composite$plant_transitions + experimental_composite$assumptions_count + experimental_composite$guarantees_count)
ggplot(experimental_composite, aes(x=m_coeff)) + 
  labs(title="Minimization distribution", subtitle="Overall") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
```


## Minimization and diagnosis time
```{r echo=FALSE}
#sive vs diagnosis time
ggplot(experimental_composite, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Size vs diagnosis time") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Minimization and minimization controllability

```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = experimental_composite$minimization_controllable_transitions / experimental_composite$plant_transitions	
m_coeff = experimental_composite$minimization_transitions / experimental_composite$plant_transitions	
ggplot(experimental_composite, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Minimization controllability vs minimization amount") +
	xlab("Minimization controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```

# Compared graphs

```{r echo=FALSE}
#rows, cols
sizediag_g_ass <- ggplot(genbuf_missing, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Genbuf.ass.") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
sizediag_safety <- ggplot(genbuf_removed, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Genbuf.safety") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
sizediag_collector <- ggplot(collector_missing, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Collector") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')	
sizediag_exploration <- ggplot(robot_removed, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Robot.safety") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
sizediag_exploration <- ggplot(robot_missing, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Robot.ass") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
plantminsize_g_ass <- ggplot(genbuf_missing, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Genbuf.ass.") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')	
plantminsize_safety <- ggplot(genbuf_removed, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Genbuf.safety") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')		
plantminsize_collector <- ggplot(collector_missing, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Collector") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') 
#+	geom_smooth(method='lm')	
plantminsize_exploration <- ggplot(robot_removed, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Robot.safety") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')	
plantminsize_exploration <- ggplot(robot_missing, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Robot.ass") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')	
c_coeff_ga = genbuf_missing$plant_controllable_transitions / genbuf_missing$plant_transitions	
m_coeff_ga = genbuf_missing$minimization_transitions / genbuf_missing$plant_transitions	
control_g_ass <- ggplot(genbuf_missing, aes(x=c_coeff_ga, y=m_coeff_ga)) +
	labs(title="Genbuf.ass") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
c_coeff_gs = genbuf_removed$plant_controllable_transitions / genbuf_removed$plant_transitions	
m_coeff_gs = genbuf_removed$minimization_transitions / genbuf_removed$plant_transitions	
control_safety <- ggplot(genbuf_removed, aes(x=c_coeff_gs, y=m_coeff_gs)) +
	labs(title="Genbuf.safety") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')
c_coeff_c = collector_missing$plant_controllable_transitions / collector_missing$plant_transitions	
m_coeff_c = collector_missing$minimization_transitions / collector_missing$plant_transitions	
control_collector <- ggplot(collector_missing, aes(x=c_coeff_c, y=m_coeff_c)) +
	labs(title="Collector") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') 
# +	geom_smooth(method='lm')
c_coeff_r = robot_removed$plant_controllable_transitions / robot_removed$plant_transitions	
m_coeff_r = robot_removed$minimization_transitions / robot_removed$plant_transitions	
control_robot <- ggplot(robot_removed, aes(x=c_coeff_r, y=m_coeff_r)) +
	labs(title="Robot.safety") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
c_coeff_r = robot_missing$plant_controllable_transitions / robot_missing$plant_transitions	
m_coeff_r = robot_missing$minimization_transitions / robot_missing$plant_transitions	
control_robot <- ggplot(robot_missing, aes(x=c_coeff_r, y=m_coeff_r)) +
	labs(title="Robot.ass") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
m_c_coeff_ga = genbuf_missing$minimization_controllable_transitions / genbuf_missing$plant_transitions	
m_m_coeff_ga = genbuf_missing$minimization_transitions / genbuf_missing$plant_transitions	
m_control_g_ass <- ggplot(genbuf_missing, aes(x=m_c_coeff_ga, y=m_m_coeff_ga)) +
	labs(title="Genbuf.ass") +
	xlab("Min. Cont.") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
m_c_coeff_gs = genbuf_removed$minimization_controllable_transitions / genbuf_removed$plant_transitions	
m_m_coeff_gs = genbuf_removed$minimization_transitions / genbuf_removed$plant_transitions	
m_control_safety <- ggplot(genbuf_removed, aes(x=m_c_coeff_gs, y=m_m_coeff_gs)) +
	labs(title="Genbuf.safety") +
	xlab("Min. Cont.") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')
m_c_coeff_c = collector_missing$minimization_controllable_transitions / collector_missing$plant_transitions	
m_m_coeff_c = collector_missing$minimization_transitions / collector_missing$plant_transitions	
m_control_collector <- ggplot(collector_missing, aes(x=m_c_coeff_c, y=m_m_coeff_c)) +
	labs(title="Collector") +
	xlab("Min. Cont.") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
  geom_smooth(method='lm')
m_c_coeff_r = robot_removed$minimization_controllable_transitions / robot_removed$plant_transitions	
m_m_coeff_r = robot_removed$minimization_transitions / robot_removed$plant_transitions	
m_control_robot_safety <- ggplot(robot_removed, aes(x=m_c_coeff_r, y=m_m_coeff_r)) +
	labs(title="Robot.safety") +
	xlab("Min. Cont.") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')
m_c_coeff_r = robot_missing$minimization_controllable_transitions / robot_missing$plant_transitions	
m_m_coeff_r = robot_missing$minimization_transitions / robot_missing$plant_transitions	
m_control_robot_g_ass <- ggplot(robot_missing, aes(x=m_c_coeff_r, y=m_m_coeff_r)) +
	labs(title="Robot.safety") +
	xlab("Min. Cont.") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')
```

```{r echo=FALSE}
grid.arrange(sizediag_g_ass, sizediag_safety, sizediag_collector, sizediag_exploration, plantminsize_g_ass, plantminsize_safety, plantminsize_collector, plantminsize_exploration, control_g_ass, control_safety, control_collector, control_robot, m_control_g_ass, m_control_safety, m_control_collector, m_control_robot_safety, m_control_robot_g_ass, ncol=4)
```

## Minimization progression
<div class="twoC">
```{r echo=FALSE}
steps_path = "/home/mariano/code/henos-automata/doc/experimental_setting/tmp_results/steps/"
steps_files = list.files(path=steps_path, pattern="*.csv")
#for (i in 1:length(steps_files)) steps_df[i] <- read.csv(steps_files[i])

effective_plots <- 0
for (i in 1:length(steps_files)){
  df <- read.csv(file=paste(steps_path, steps_files[i], sep=''))
  if(length(df$step) < 2){
    next
  }
  effective_plots <- effective_plots + 1
}
#layout(matrix(1:effective_plots*2,nc=2, nr= effective_plots,byr=T))
for (i in 1:length(steps_files)){
  df <- read.csv(file=paste(steps_path, steps_files[i], sep=''))
  if(length(df$step) < 2){
    next
  }
  time_plot <- ggplot(df, aes(x=step, y=time, group=i)) +
  geom_line(linetype="dashed", color="blue", size=1.2)+
  geom_point(color="red", size=3) + 
  labs(title=steps_files[i]) +
	xlab("Steps") +
	ylab("Time (s)") 
  print(time_plot)
  size_plot <- ggplot(df, aes(x=step, y=size, group=i)) +
  geom_line(linetype="dashed", color="blue", size=1.2)+
  geom_point(color="red", size=3) + 
  labs(title=steps_files[i]) +
	xlab("Steps") +
	ylab(expression(paste("|",Delta[paste("E","'")],"|")))
  print(size_plot)  
}


```
</div>
<div class="clearer"></div>


# Composite graphs

## Minimization distribution

```{r echo=FALSE}
experimental_composite$m_coeff = experimental_composite$minimization_transitions / experimental_composite$plant_transitions
experimental_composite$relative_time = experimental_composite$diagnosis_time / experimental_composite$plant_transitions
experimental_composite$relative_time_liveness = experimental_composite$diagnosis_time / (experimental_composite$plant_transitions + experimental_composite$assumptions_count + experimental_composite$guarantees_count)
ggplot(experimental_composite, aes(x=m_coeff)) + 
  labs(title="Minimization distribution", subtitle="Overall") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
ggplot(experimental_composite, aes(x=relative_time)) + 
  labs(title=expression(paste("Min. time / |",Delta["E"],"|")), subtitle="Overall") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
ggplot(experimental_composite, aes(x=relative_time_liveness)) + 
  labs(title=expression(paste("Min. time / (|",Delta["E"],"|* liveness)")), subtitle="Overall") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
genbuf_missing$m_coeff = genbuf_missing$minimization_transitions / genbuf_missing$plant_transitions
genbuf_missing$relative_time = genbuf_missing$diagnosis_time / genbuf_missing$plant_transitions
genbuf_missing$relative_time_liveness = genbuf_missing$diagnosis_time / (genbuf_missing$plant_transitions + genbuf_missing$assumptions_count + genbuf_missing$guarantees_count)
hist_g_ass <- ggplot(genbuf_missing, aes(x=m_coeff)) + 
  labs(title="Minimization distribution", subtitle="Genbuf miss. ass.") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_g_ass_rel <- ggplot(genbuf_missing, aes(x=relative_time)) + 
  labs(title=expression(paste("Min. time / |",Delta["E"],"|")), subtitle="Genbuf miss. ass.") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_g_ass_rel_liv <- ggplot(genbuf_missing, aes(x=relative_time_liveness)) + 
  labs(title=expression(paste("Min. time / (|",Delta["E"],"|* liveness)")), subtitle="Genbuf miss. ass.") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
genbuf_removed$m_coeff = genbuf_removed$minimization_transitions / genbuf_removed$plant_transitions
genbuf_removed$relative_time = genbuf_removed$diagnosis_time / genbuf_removed$plant_transitions
genbuf_removed$relative_time_liveness = genbuf_removed$diagnosis_time / (genbuf_removed$plant_transitions + genbuf_removed$assumptions_count + genbuf_removed$guarantees_count)
hist_g_safety <- ggplot(genbuf_removed, aes(x=m_coeff)) + 
  labs(title="Minimization distribution", subtitle="Genbuf removed env. safety") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_g_safety_rel <- ggplot(genbuf_removed, aes(x=relative_time)) + 
  labs(title=expression(paste("Min. time / |",Delta["E"],"|")), subtitle="Genbuf removed env. safety") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_g_safety_rel_liv<- ggplot(genbuf_removed, aes(x=relative_time_liveness)) + 
  labs(title=expression(paste("Min. time / (|",Delta["E"],"|* liveness)")), subtitle="Genbuf removed env. safety") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
collector_missing$m_coeff = collector_missing$minimization_transitions / collector_missing$plant_transitions
collector_missing$relative_time = collector_missing$diagnosis_time / collector_missing$plant_transitions
collector_missing$relative_time_liveness = collector_missing$diagnosis_time / (collector_missing$plant_transitions + collector_missing$assumptions_count + collector_missing$guarantees_count)
hist_collector <- ggplot(collector_missing, aes(x=m_coeff)) + 
  labs(title="Minimization distribution", subtitle="Collector") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_collector_rel <- ggplot(collector_missing, aes(x=relative_time)) + 
  labs(title=expression(paste("Min. time / |",Delta["E"],"|")), subtitle="Collector") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_collector_rel_liv <- ggplot(collector_missing, aes(x=relative_time_liveness)) + 
  labs(title=expression(paste("Min. time / (|",Delta["E"],"|* liveness)")), subtitle="Collector") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
robot_removed$m_coeff = robot_removed$minimization_transitions / robot_removed$plant_transitions
robot_removed$relative_time = robot_removed$diagnosis_time / robot_removed$plant_transitions
robot_removed$relative_time_liveness = robot_removed$diagnosis_time / (robot_removed$plant_transitions + robot_removed$assumptions_count + robot_removed$guarantees_count)
hist_robot <- ggplot(robot_removed, aes(x=m_coeff)) + 
  labs(title="Minimization distribution", subtitle="Robot Explorer env. safety") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_robot_rel <- ggplot(robot_removed, aes(x=relative_time)) + 
  labs(title=expression(paste("Min. time / |",Delta["E"],"|")), subtitle="Robot Explorer") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_robot_rel_liv <- ggplot(robot_removed, aes(x=relative_time_liveness)) + 
  labs(title=expression(paste("Min. time / (|",Delta["E"],"|* liveness)")), subtitle="Robot Explorer") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
robot_missing$m_coeff = robot_missing$minimization_transitions / robot_missing$plant_transitions
robot_missing$relative_time = robot_missing$diagnosis_time / robot_missing$plant_transitions
robot_missing$relative_time_liveness = robot_missing$diagnosis_time / (robot_missing$plant_transitions + robot_missing$assumptions_count + robot_missing$guarantees_count)
hist_robot <- ggplot(robot_missing, aes(x=m_coeff)) + 
  labs(title="Minimization distribution", subtitle="Robot Explorer miss. ass.") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_robot_rel <- ggplot(robot_missing, aes(x=relative_time)) + 
  labs(title=expression(paste("Min. time / |",Delta["E"],"|")), subtitle="Robot Explorer") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
hist_robot_rel_liv <- ggplot(robot_missing, aes(x=relative_time_liveness)) + 
  labs(title=expression(paste("Min. time / (|",Delta["E"],"|* liveness)")), subtitle="Robot Explorer") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")

grid.arrange(hist_g_ass, hist_g_safety, hist_collector, hist_robot, ncol=2)

grid.arrange(hist_g_ass_rel, hist_g_safety_rel, hist_collector_rel, hist_robot_rel, ncol=2)

grid.arrange(hist_g_ass_rel_liv, hist_g_safety_rel_liv, hist_collector_rel_liv, hist_robot_rel_liv, ncol=2)
```

## Minimization and controllability
```{r echo=FALSE}
#sive vs diagnosis time
ggplot(experimental_composite, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Size vs diagnosis time") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```
## Minimization and controllability
```{r echo=FALSE}
#plant size vs minimization time	
ggplot(experimental_composite, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Plant size vs minimization size") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') 
```

```{r echo=FALSE}
#plant size vs minimization time w labels
hidden <- ggplot(experimental_composite, aes(x=plant_transitions, y=minimization_transitions, label=name)) +
	labs(title="Plant size vs minimization size") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_text(aes(label=as.character(name)),hjust=0,vjust=0) +
	geom_smooth(method='lm')
```
## Minimization and plant controllability
```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = experimental_composite$plant_controllable_transitions / experimental_composite$plant_transitions	
m_coeff = experimental_composite$minimization_transitions / experimental_composite$plant_transitions	
ggplot(experimental_composite, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Plant controllability vs minimization amount") +
	xlab("Plant controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') 
```

```{r echo=FALSE}
#plant controllability vs minimization amount w labels
c_coeff = experimental_composite$plant_controllable_transitions / experimental_composite$plant_transitions	
m_coeff = experimental_composite$minimization_transitions / experimental_composite$plant_transitions	
hidden <- ggplot(experimental_composite, aes(x=c_coeff, y=m_coeff, label=name)) +
	labs(title="Plant controllability vs minimization amount") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_text(aes(label=as.character(name)),hjust=0,vjust=0) +
	geom_smooth(method='lm')	
    
```

## Minimization and minimization controllability

```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = experimental_composite$minimization_controllable_transitions / experimental_composite$plant_transitions	
m_coeff = experimental_composite$minimization_transitions / experimental_composite$plant_transitions	
ggplot(experimental_composite, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Minimization controllability vs minimization amount") +
	xlab("Minimization controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```


# Genbuf missing assumption

## Minimization and controllability

```{r echo=FALSE}
#sive vs diagnosis time
ggplot(genbuf_missing, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Size vs diagnosis time") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant vs minimization time

```{r echo=FALSE}
#plant size vs minimization time	
ggplot(genbuf_missing, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Plant size vs minimization size") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant controllability vs minimization rate

```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = genbuf_missing$plant_controllable_transitions / genbuf_missing$plant_transitions	
m_coeff = genbuf_missing$minimization_transitions / genbuf_missing$plant_transitions	
ggplot(genbuf_missing, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Plant controllability vs minimization amount") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```

# Genbuf removed env. safety

## Minimization and controllability

```{r echo=FALSE}
#sive vs diagnosis time
ggplot(genbuf_removed, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Size vs diagnosis time") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant vs minimization time

```{r echo=FALSE}
#plant size vs minimization time	
ggplot(genbuf_removed, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Plant size vs minimization size") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant controllability vs minimization rate

```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = genbuf_removed$plant_controllable_transitions / genbuf_removed$plant_transitions	
m_coeff = genbuf_removed$minimization_transitions / genbuf_removed$plant_transitions	
ggplot(genbuf_removed, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Plant controllability vs minimization amount") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```


# Collector missing assumption

## Minimization and controllability

```{r echo=FALSE}
#sive vs diagnosis time
ggplot(collector_missing, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Size vs diagnosis time") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant vs minimization time

```{r echo=FALSE}
#plant size vs minimization time	
ggplot(collector_missing, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Plant size vs minimization size") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant controllability vs minimization rate

```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = collector_missing$plant_controllable_transitions / collector_missing$plant_transitions	
m_coeff = collector_missing$minimization_transitions / collector_missing$plant_transitions	
ggplot(collector_missing, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Plant controllability vs minimization amount") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```


# Exploration robot removed safety

## Minimization and controllability

```{r echo=FALSE}
#sive vs diagnosis time
ggplot(robot_removed, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Size vs diagnosis time") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant vs minimization time

```{r echo=FALSE}
#plant size vs minimization time	
ggplot(robot_removed, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Plant size vs minimization size") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant controllability vs minimization rate

```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = robot_removed$plant_controllable_transitions / robot_removed$plant_transitions	
m_coeff = robot_removed$minimization_transitions / robot_removed$plant_transitions	
ggplot(robot_removed, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Plant controllability vs minimization amount") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```


# Exploration robot missing assumption

## Minimization and controllability

```{r echo=FALSE}
#sive vs diagnosis time
ggplot(robot_missing, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Size vs diagnosis time") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant vs minimization time

```{r echo=FALSE}
#plant size vs minimization time	
ggplot(robot_missing, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Plant size vs minimization size") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Plant controllability vs minimization rate

```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = robot_missing$plant_controllable_transitions / robot_missing$plant_transitions	
m_coeff = robot_missing$minimization_transitions / robot_missing$plant_transitions	
ggplot(robot_missing, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Plant controllability vs minimization amount") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```
