---
title: "Behavior Minimization"
author: "Mariano Cerrutti"
date: "5/26/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      results= "asis")
#install.packages("dplyr")
#install.packages("magrittr")
#install.packages("ggplot2")
#install.packages("jsonlite")
library(dplyr)
library(magrittr)
library(ggplot2)
library(jsonlite)
library(gridExtra)
library(grid)
library(lattice)
library(knitr)
library(scales)
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
experimental_composite <- read.csv(file='/home/mariano/code/henos-automata/doc/experimental_setting/tmp_results/general_data_composite_ctrl.csv')
genbuf_missing <- subset(experimental_composite, grepl("automaton_missing_assumption", name, fixed=TRUE))
genbuf_removed <- subset(experimental_composite, grepl("automaton_removed_env_safety", name, fixed=TRUE))
collector_missing <- subset(experimental_composite, grepl("v1_missing_assumption", name, fixed=TRUE))
robot_samples <- subset(experimental_composite, grepl("robot", name, fixed=TRUE))

```
<style type="text/css">
.twoC {width: 100%}
.clearer {clear: both}
.twoC .table {max-width: 50%; float: right}
.twoC img {max-width: 50%; float: left}
table {
  margin: auto;
  border-top: 1px solid #666;
  border-bottom: 1px solid #666;
}
table thead th { border-bottom: 1px solid #ddd; }
th, td { padding: 5px; }
thead, tfoot, tr:nth-child(even) { background: #eee; }
pre{display:none;}
</style>

# Selected Graphs

## General Table

Controller sizes go from `r min(experimental_composite$ctrl_size)` transitions up to `r max(experimental_composite$ctrl_size)`.
Minimization reduction relative to controller goes from `r max(experimental_composite$minimization_transitions / experimental_composite$ctrl_size)` up to `r min(experimental_composite$minimization_transitions / experimental_composite$ctrl_size)`.

```{r echo=FALSE}
times_table <- experimental_composite[c(1,7)]
times_table$liveness_count <- experimental_composite$guarantees_count + experimental_composite$assumptions_count
times_table$plant_transitions <- experimental_composite$plant_transitions
times_table$minimization_transitions <- experimental_composite$minimization_transitions
times_table$reduction <- experimental_composite$minimization_transitions / experimental_composite$ctrl_size
times_table$ctrl_size <- experimental_composite$ctrl_size
times_table$ctrl_comp_size <- experimental_composite$ctrl_comp_size
times_table <- times_table %>%
  group_by(name) %>%
  summarize(diag <- mean(diagnosis_time), liveness <- max(liveness_count), plant_trans <- max(plant_transitions),
            min_trans <- max(minimization_transitions), red <- mean(reduction), c_size <- max(ctrl_size), c_comp_size <- max(ctrl_comp_size))
kable(times_table, caption = "Times table", col.names=c("Specification","Diagnosis(s)","Liveness fluents", "Plant transitions", "Min. transitions","Minimization pct.(%)", "Controller size", "C || E' size"))
```

## Controller and Minimization size
```{r echo=FALSE}
#sive vs diagnosis time
ggplot(experimental_composite, aes(x=minimization_transitions, y=ctrl_size)) +
	labs(title="Controller vs min. size") +
	xlab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	ylab(expression(paste("|",Delta["C"],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Controller composition w. min. and Minimization size
```{r echo=FALSE}
#sive vs diagnosis time
ggplot(experimental_composite, aes(x=minimization_transitions, y=ctrl_comp_size)) +
	labs(title="C || E' vs min. size") +
	xlab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	ylab(expression(paste("|",Delta[paste("C","|","|","E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Controller size and diagnosis time
```{r echo=FALSE}
#sive vs diagnosis time
ggplot(experimental_composite, aes(x=ctrl_size, y=diagnosis_time)) +
	labs(title="Controller vs min. size") +
	xlab(expression(paste("|",Delta["C"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Minimization and diagnosis time
```{r echo=FALSE}
#sive vs diagnosis time
ggplot(experimental_composite, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Size vs diagnosis time") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Minimization and minimization controllability

```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = experimental_composite$minimization_controllable_transitions / experimental_composite$plant_transitions	
m_coeff = experimental_composite$minimization_transitions / experimental_composite$plant_transitions	
ggplot(experimental_composite, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Minimization controllability vs minimization amount") +
	xlab("Minimization controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```
