---
title: "Behavior Minimization"
author: "Mariano Cerrutti"
date: "5/26/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      results= "asis")
#install.packages("dplyr")
#install.packages("magrittr")
#install.packages("ggplot2")
#install.packages("jsonlite")
#install.packages("plot3D")
library(dplyr)
library(magrittr)
library(ggplot2)
library(jsonlite)
library(gridExtra)
library(grid)
library(lattice)
library(knitr)
library(scales)
library(plot3D)
library(stringr)
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
#experimental_composite <- read.csv(file='/home/mariano/code/henos-automata/doc/experimental_setting/tmp_results/general_data_composite.csv')
experimental_composite <- read.csv(file='/home/mariano/code/henos-automata/doc/experimental_setting/tmp_results/unrealizable_data_composite.csv')
genbuf_missing <- subset(experimental_composite, grepl("automaton_missing_assumption", name, fixed=TRUE))
genbuf_removed <- subset(experimental_composite, grepl("automaton_removed_env_safety", name, fixed=TRUE))
collector_missing <- subset(experimental_composite, grepl("v1_missing_assumption", name, fixed=TRUE))
robot_samples <- subset(experimental_composite, grepl("robot", name, fixed=TRUE))

```
<style type="text/css">
.twoC {width: 100%}
.clearer {clear: both}
.twoC .table {max-width: 50%; float: right}
.twoC img {max-width: 50%; float: left}
table {
  margin: auto;
  border-top: 1px solid #666;
  border-bottom: 1px solid #666;
}
table thead th { border-bottom: 1px solid #ddd; }
th, td { padding: 5px; }
thead, tfoot, tr:nth-child(even) { background: #eee; }
pre{display:none;}
</style>

# Selected Graphs

## General Table

Specification sizes go from `r min(experimental_composite$plant_transitions)` transitions up to `r max(experimental_composite$plant_transitions)`.
Minimization reduction goes from `r max(experimental_composite$minimization_transitions / experimental_composite$plant_transitions)` up to `r min(experimental_composite$minimization_transitions / experimental_composite$plant_transitions)`.

```{r echo=FALSE}
times_table <- experimental_composite[c(1,7)]
times_table$liveness_count <- experimental_composite$guarantees_count + experimental_composite$assumptions_count
times_table$plant_transitions <- experimental_composite$plant_transitions
times_table$minimization_transitions <- experimental_composite$minimization_transitions
times_table$reduction <- experimental_composite$minimization_transitions / experimental_composite$plant_transitions
times_table$steps <- experimental_composite$diagnosis_steps
times_table <- times_table %>%
  group_by(name) %>%
  summarize(diag <- mean(diagnosis_time), liveness <- max(liveness_count), plant_trans <- max(plant_transitions),
            min_trans <- max(minimization_transitions), red <- mean(reduction), steps <- max(steps))
kable(times_table, caption = "Times table", col.names=c("Specification","Diagnosis(s)","Liveness fluents", "Plant transitions", "Min. transitions","Minimization pct.(%)","Min. steps"))
```

## Minimization distribution (overall)

```{r echo=FALSE}
experimental_composite$m_coeff = experimental_composite$minimization_transitions / experimental_composite$plant_transitions
experimental_composite$relative_time = experimental_composite$diagnosis_time / experimental_composite$plant_transitions
experimental_composite$relative_time_liveness = experimental_composite$diagnosis_time / (experimental_composite$plant_transitions + experimental_composite$assumptions_count + experimental_composite$guarantees_count)
ggplot(experimental_composite, aes(x=m_coeff)) + 
  labs(title="Minimization distribution", subtitle="Overall") +
  xlab("Minimization rate") +
  ylab("Count") + 
    geom_histogram(color="black",fill="white")
```


## Minimization and diagnosis time
```{r echo=FALSE}
#sive vs diagnosis time
ggplot(experimental_composite, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Size vs diagnosis time") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Minimization and minimization controllability

```{r echo=FALSE}
#plant controllability vs minimization amount
c_coeff = experimental_composite$minimization_controllable_transitions / experimental_composite$plant_transitions	
m_coeff = experimental_composite$minimization_transitions / experimental_composite$plant_transitions	
ggplot(experimental_composite, aes(x=c_coeff, y=m_coeff)) +
	labs(title="Minimization controllability vs minimization amount") +
	xlab("Minimization controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```

# Sequntialization of CLTS structures

```{r echo=FALSE}
seq_composite <- read.csv(file='/home/mariano/code/henos-automata/doc/experimental_setting/tmp_results/seq_data_composite.csv')

seq_composite_genbuf_4 <- dplyr::filter(seq_composite, grepl("genbuf_4",filename))
seq_composite_arbiter_3 <- dplyr::filter(seq_composite, grepl("arbiter_3",filename))

seq_composite_game <- dplyr::filter(seq_composite, !grepl("intrlvd",filename) & !grepl("seq",filename))
seq_composite_intrlvd <- dplyr::filter(seq_composite, grepl("intrlvd",filename))
seq_composite_seq <- dplyr::filter(seq_composite, grepl("seq",filename))
seq_composite_game_intrlvd_conform <- seq_composite_game[-c(21,22,23,27),]

seq_composite_game$seq_states <- seq_composite_seq$states_count
seq_composite_game$seq_transitions <- seq_composite_seq$transitions_count
seq_composite_game$states_ratio <- seq_composite_game$states_count / seq_composite_seq$states_count
seq_composite_game$transitions_ratio <- seq_composite_game$transitions_count / seq_composite_seq$transitions_count;
seq_composite_game$states_ratio_vs_mean_signals <- seq_composite_game$mean_signals_t / (seq_composite_game$states_count / seq_composite_seq$states_count);
seq_composite_game$trans_times_mean_signals <- (seq_composite_game$mean_signals_t+2) * seq_composite_game$transitions_count;
seq_composite_game$trans_times_mean_signals_vs_seq_states <- (seq_composite_game$seq_states - seq_composite_game$states_count) / seq_composite_game$trans_times_mean_signals;
seq_composite_game$trans_vs_states <- seq_composite_game$transitions_count / seq_composite_game$states_count;

seq_composite_game_intrlvd_conform$intrlvd_states <- seq_composite_intrlvd$states_count
seq_composite_game_intrlvd_conform$intrlvd_transitions <- seq_composite_intrlvd$transitions_count
seq_composite_game_intrlvd_conform$states_ratio <- seq_composite_game_intrlvd_conform$states_count / seq_composite_intrlvd$states_count
seq_composite_game_intrlvd_conform$transitions_ratio <- seq_composite_game_intrlvd_conform$transitions_count / seq_composite_intrlvd$transitions_count;
seq_composite_game_intrlvd_conform$states_ratio_vs_mean_signals <- seq_composite_game_intrlvd_conform$mean_signals_t / (seq_composite_game_intrlvd_conform$states_count / seq_composite_intrlvd$states_count);
seq_composite_game_intrlvd_conform$trans_times_mean_signals <- (seq_composite_game_intrlvd_conform$mean_signals_t+2) * seq_composite_game_intrlvd_conform$transitions_count;
seq_composite_game_intrlvd_conform$trans_times_mean_signals_vs_intrlvd_states <- (seq_composite_game_intrlvd_conform$intrlvd_states - seq_composite_game_intrlvd_conform$states_count) / seq_composite_game_intrlvd_conform$trans_times_mean_signals;
seq_composite_game_intrlvd_conform$trans_vs_states <- seq_composite_game_intrlvd_conform$transitions_count / seq_composite_game_intrlvd_conform$states_count;

seq_composite_game_no_robot <- dplyr::filter(seq_composite_game, !grepl("robot",filename))
seq_composite_game_robot <- dplyr::filter(seq_composite_game, grepl("robot",filename))
seq_composite_game_intrlvd_conform_no_robot <- dplyr::filter(seq_composite_game_intrlvd_conform, !grepl("robot",filename))
seq_composite_game_intrlvd_conform_robot <- dplyr::filter(seq_composite_game_intrlvd_conform, !grepl("robot",filename))
```

## Reduction table (concurrent vs sequential)

```{r echo=FALSE}
#, col.names=c("Specification","Diagnosis(s)","Liveness fluents", "Plant transitions", "Min. transitions","Minimization pct.(%)","Min. steps")
table_seq_composite_game_no_robot <- subset(seq_composite_game_no_robot, select = c(filename, states_count, seq_states, states_ratio, transitions_count, seq_transitions, transitions_ratio, mean_delta_s, mean_signals_t, trans_times_mean_signals, trans_times_mean_signals_vs_seq_states, trans_vs_states))
table_seq_composite_game_no_robot$filename <- str_replace_all(table_seq_composite_game_no_robot$filename, "/tmp/", "")
table_seq_composite_game_no_robot$filename <- str_replace_all(table_seq_composite_game_no_robot$filename, ".diag", "")
table_seq_composite_game_no_robot$filename <- str_replace_all(table_seq_composite_game_no_robot$filename, ".game", "")
table_seq_composite_game_no_robot$filename <- str_replace_all(table_seq_composite_game_no_robot$filename, ".fsp", "")
table_seq_composite_game_no_robot$filename <- str_replace_all(table_seq_composite_game_no_robot$filename, "_", " ")
kable(table_seq_composite_game_no_robot, caption = "Concurrent vs seq", col.names=c("Specification","#States","#Seq. states","#States/#Seq. states", "#Transitions", "#Seq. trans", "#Trans/#Seq, Trans","Mean out(s)","Mean signals per trans.", "#Trans x mean signals", "#Seq. states/#Trans x mean signals", "#Trans./#States"))
```


## Explaining sequential size correlation (event based)

```{r echo=FALSE}
ggplot(table_seq_composite_game_no_robot, aes(x=trans_times_mean_signals_vs_seq_states, y=trans_vs_states, label=filename)) +
  geom_point() +geom_text(aes(label=filename),hjust=0, vjust=0)+
  labs(title="Seq. size explanation 1") +
  xlab("#Seq. states/#Trans x mean signals") +
  ylab("#Trans./#States") +	
  geom_point(color='red') +	
  
	geom_smooth(method='lm')

ggplot(table_seq_composite_game_no_robot, aes(x=1/states_ratio, y=trans_vs_states, label=filename)) +
  geom_point() +geom_text(aes(label=filename),hjust=0, vjust=0)+
  labs(title="Seq. size explanation 2") +
  xlab("#Seq. #States/States") +
  ylab("#Trans./#States") +	
  geom_point(color='red') +	
    scale_y_log10() +
    scale_x_log10() +
	geom_smooth(method='lm')
```

## Reduction table (concurrent vs interleaved)

```{r echo=FALSE}
#, col.names=c("Specification","Diagnosis(s)","Liveness fluents", "Plant transitions", "Min. transitions","Minimization pct.(%)","Min. steps")
table_intrlvd_composite_game_no_robot <- subset(seq_composite_game_intrlvd_conform_no_robot, select = c(filename, states_count, intrlvd_states, states_ratio, transitions_count, intrlvd_transitions, transitions_ratio, mean_delta_s, mean_signals_t, trans_times_mean_signals, trans_times_mean_signals_vs_intrlvd_states, trans_vs_states))
table_intrlvd_composite_game_no_robot$filename <- str_replace_all(table_intrlvd_composite_game_no_robot$filename, "/tmp/", "")
table_intrlvd_composite_game_no_robot$filename <- str_replace_all(table_intrlvd_composite_game_no_robot$filename, ".diag", "")
table_intrlvd_composite_game_no_robot$filename <- str_replace_all(table_intrlvd_composite_game_no_robot$filename, ".game", "")
table_intrlvd_composite_game_no_robot$filename <- str_replace_all(table_intrlvd_composite_game_no_robot$filename, ".fsp", "")
table_intrlvd_composite_game_no_robot$filename <- str_replace_all(table_intrlvd_composite_game_no_robot$filename, "_", " ")
kable(table_intrlvd_composite_game_no_robot, caption = "Concurrent vs interleaved", col.names=c("Specification","#States","#Intrlvd. States","#States/#Intrlvd. States", "#Transitions","#Intrlvd. Trans", "#Trans/#Intrlvd. Trans","Mean out(s)","Mean signals per trans.", "#Trans x mean signals", "#Intrlvd. states/#Trans x mean signals", "#Trans./#States"))
```

## Mean signal count vs space reduction (seq, signal based)

```{r echo=FALSE}
x <- seq_composite_game_no_robot$states_count
y <- seq_composite_game_no_robot$states_ratio
z <- seq_composite_game_no_robot$mean_signals_t
# Compute the linear regression 
fit <- lm(z ~ x + y)
# create a grid from the x and y values (min to max) and predict values for every point
# this will become the regression plane
grid.lines = 20
x.pred <- seq(min(x), max(x), length.out = grid.lines)
y.pred <- seq(min(y), max(y), length.out = grid.lines)
xy <- expand.grid( x = x.pred, y = y.pred)
z.pred <- matrix(predict(fit, newdata = xy), 
                 nrow = grid.lines, ncol = grid.lines)
# create the fitted points for droplines to the surface
fitpoints <- predict(fit)
# scatter plot with regression plane
scatter3D(x, y, z, pch = 19, cex = 1,colvar = NULL, col="red", theta = -30, phi = 0, bty="b",
          xlab = "|S|", ylab = "|S|/|S'|", zlab = "mean sig. x trans.", surf = list(x = x.pred, y = y.pred, z = z.pred,  
                      facets = TRUE, fit = fitpoints, col=ramp.col (col = c("dodgerblue3","seagreen2"), n = 300, alpha=0.5), border="black"), main = "Mean signal count vs space reduction (seq, signal based)")
 
```

## Mean signal count vs space reduction (seq, signal based)

```{r echo=FALSE}
x <- seq_composite_game_no_robot$transitions_count
y <- seq_composite_game_no_robot$transitions_ratio
z <- seq_composite_game_no_robot$mean_signals_t
# Compute the linear regression 
fit <- lm(z ~ x + y)
# create a grid from the x and y values (min to max) and predict values for every point
# this will become the regression plane
grid.lines = 20
x.pred <- seq(min(x), max(x), length.out = grid.lines)
y.pred <- seq(min(y), max(y), length.out = grid.lines)
xy <- expand.grid( x = x.pred, y = y.pred)
z.pred <- matrix(predict(fit, newdata = xy), 
                 nrow = grid.lines, ncol = grid.lines)
# create the fitted points for droplines to the surface
fitpoints <- predict(fit)
# scatter plot with regression plane
scatter3D(x, y, z, pch = 19, cex = 1,colvar = NULL, col="red", theta = -30, phi = 0, bty="b",
          xlab = "|Delta|", ylab = "|Delta|/|Delta'|", zlab = "mean sig. x trans.", surf = list(x = x.pred, y = y.pred, z = z.pred,  
                      facets = TRUE, fit = fitpoints, col=ramp.col (col = c("dodgerblue3","seagreen2"), n = 300, alpha=0.5), border="black"), main = "Mean signal count vs trans. reduction (seq, signal based)")
 
```

## Sequential translation (signal based)

```{r echo=FALSE}


ggplot(seq_composite_game_no_robot, aes(x=states_count, y=states_ratio)) +
  labs(title="Seq. states reduction ratio (signal based)") +
  xlab("|S_E|") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red') +	
	geom_smooth(method='lm')

ggplot(seq_composite_game_no_robot, aes(x=transitions_count, y=transitions_ratio)) +
  labs(title="Seq. transition reduction ratio (signal based)") +
  xlab("|Delta_E|") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red')  +	
	geom_smooth(method='lm')

ggplot(seq_composite_game_no_robot, aes(x=mean_signals_t, y=states_ratio)) +
  labs(title="Seq. states reduction ratio vs mean signals") +
  xlab("mean(signals per trans.)") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red')  +	
	geom_smooth(method='lm')

ggplot(seq_composite_game_no_robot, aes(x=mean_signals_t, y=transitions_ratio)) +
  labs(title="Seq. transition reduction ratio vs mean signals") +
  xlab("mean(signals per trans.)") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red')  +	
	geom_smooth(method='lm')
```

## Sequential translation (event based)

```{r echo=FALSE}
ggplot(seq_composite_game_robot, aes(x=states_count, y=states_ratio)) +
  labs(title="Seq. states reduction ratio (event based)") +
  xlab("|S_E|") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red') +	
	geom_smooth(method='lm')

ggplot(seq_composite_game_robot, aes(x=transitions_count, y=transitions_ratio)) +
  labs(title="Seq. transition reduction ratio (event based)") +
  xlab("|Delta_E|") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Interleaved translation(signal based)

```{r echo=FALSE}
ggplot(seq_composite_game_intrlvd_conform_no_robot, aes(x=states_count, y=states_ratio)) +
  labs(title="Seq. states reduction ratio (signal based)") +
  xlab("|S_E|") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red') +	
	geom_smooth(method='lm')

ggplot(seq_composite_game_intrlvd_conform_no_robot, aes(x=transitions_count, y=transitions_ratio)) +
  labs(title="Seq. transition reduction ratio (signal based)") +
  xlab("|Delta_E|") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red') +	
	geom_smooth(method='lm')
```

## Interleaved translation (event based)
```{r echo=FALSE}

ggplot(seq_composite_game_intrlvd_conform_robot, aes(x=states_count, y=states_ratio)) +
  labs(title="Seq. states reduction ratio (event based)") +
  xlab("|S_E|") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red') +	
	geom_smooth(method='lm')

ggplot(seq_composite_game_intrlvd_conform_robot, aes(x=transitions_count, y=transitions_ratio)) +
  labs(title="Seq. transition reduction ratio (event based)") +
  xlab("|Delta_E|") +
  ylab("Reduction") +
  scale_y_log10() +
  scale_x_log10() +	
  geom_point(color='red') +	
	geom_smooth(method='lm')
```

# Compared graphs

```{r echo=FALSE}
#rows, cols
sizediag_g_ass <- ggplot(genbuf_missing, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Genbuf.ass.") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
sizediag_safety <- ggplot(genbuf_removed, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Genbuf.safety") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
sizediag_collector <- ggplot(collector_missing, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Collector") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')	
sizediag_exploration <- ggplot(robot_samples, aes(x=plant_transitions, y=diagnosis_time)) +
	labs(title="Robot") +
	xlab(expression(paste("|",Delta["E"],"|"))) +
	ylab("Diagnosis time (s)") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')
plantminsize_g_ass <- ggplot(genbuf_missing, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Genbuf.ass.") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')	
plantminsize_safety <- ggplot(genbuf_removed, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Genbuf.safety") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')		
plantminsize_collector <- ggplot(collector_missing, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Collector") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') 
#+	geom_smooth(method='lm')	
plantminsize_exploration <- ggplot(robot_samples, aes(x=plant_transitions, y=minimization_transitions)) +
	labs(title="Robot") +
	xlab(expression(paste("|",Delta[E],"|"))) +
	ylab(expression(paste("|",Delta[paste("E","'")],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')	
c_coeff_ga = genbuf_missing$plant_controllable_transitions / genbuf_missing$plant_transitions	
m_coeff_ga = genbuf_missing$minimization_transitions / genbuf_missing$plant_transitions	
control_g_ass <- ggplot(genbuf_missing, aes(x=c_coeff_ga, y=m_coeff_ga)) +
	labs(title="Genbuf.ass") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
c_coeff_gs = genbuf_removed$plant_controllable_transitions / genbuf_removed$plant_transitions	
m_coeff_gs = genbuf_removed$minimization_transitions / genbuf_removed$plant_transitions	
control_safety <- ggplot(genbuf_removed, aes(x=c_coeff_gs, y=m_coeff_gs)) +
	labs(title="Genbuf.safety") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')
c_coeff_c = collector_missing$plant_controllable_transitions / collector_missing$plant_transitions	
m_coeff_c = collector_missing$minimization_transitions / collector_missing$plant_transitions	
control_collector <- ggplot(collector_missing, aes(x=c_coeff_c, y=m_coeff_c)) +
	labs(title="Collector") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') 
# +	geom_smooth(method='lm')
c_coeff_r = robot_samples$plant_controllable_transitions / robot_samples$plant_transitions	
m_coeff_r = robot_samples$minimization_transitions / robot_samples$plant_transitions	
control_robot <- ggplot(robot_samples, aes(x=c_coeff_r, y=m_coeff_r)) +
	labs(title="Robot") +
	xlab("Controllability") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
m_c_coeff_ga = genbuf_missing$minimization_controllable_transitions / genbuf_missing$plant_transitions	
m_m_coeff_ga = genbuf_missing$minimization_transitions / genbuf_missing$plant_transitions	
m_control_g_ass <- ggplot(genbuf_missing, aes(x=m_c_coeff_ga, y=m_m_coeff_ga)) +
	labs(title="Genbuf.ass") +
	xlab("Min. Cont.") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
m_c_coeff_gs = genbuf_removed$minimization_controllable_transitions / genbuf_removed$plant_transitions	
m_m_coeff_gs = genbuf_removed$minimization_transitions / genbuf_removed$plant_transitions	
m_control_safety <- ggplot(genbuf_removed, aes(x=m_c_coeff_gs, y=m_m_coeff_gs)) +
	labs(title="Genbuf.safety") +
	xlab("Min. Cont.") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')
m_c_coeff_c = collector_missing$minimization_controllable_transitions / collector_missing$plant_transitions	
m_m_coeff_c = collector_missing$minimization_transitions / collector_missing$plant_transitions	
m_control_collector <- ggplot(collector_missing, aes(x=m_c_coeff_c, y=m_m_coeff_c)) +
	labs(title="Collector") +
	xlab("Min. Cont.") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
  geom_smooth(method='lm')
m_c_coeff_r = robot_samples$minimization_controllable_transitions / robot_samples$plant_transitions	
m_m_coeff_r = robot_samples$minimization_transitions / robot_samples$plant_transitions	
m_control_robot <- ggplot(robot_samples, aes(x=m_c_coeff_r, y=m_m_coeff_r)) +
	labs(title="Robot") +
	xlab("Min. Cont.") +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	
```

```{r echo=FALSE}
grid.arrange(sizediag_g_ass, sizediag_safety, sizediag_collector, sizediag_exploration, plantminsize_g_ass, plantminsize_safety, plantminsize_collector, plantminsize_exploration, control_g_ass, control_safety, control_collector, control_robot, m_control_g_ass, m_control_safety, m_control_collector, m_control_robot, ncol=4)
```

## Minimization progression
<div class="twoC">
```{r echo=FALSE}
steps_path = "/home/mariano/code/henos-automata/doc/experimental_setting/tmp_results/steps/"
steps_files = list.files(path=steps_path, pattern="*.csv")
#for (i in 1:length(steps_files)) steps_df[i] <- read.csv(steps_files[i])

effective_plots <- 0
for (i in 1:length(steps_files)){
  df <- read.csv(file=paste(steps_path, steps_files[i], sep=''))
  if(length(df$step) < 2){
    next
  }
  effective_plots <- effective_plots + 1
}
#layout(matrix(1:effective_plots*2,nc=2, nr= effective_plots,byr=T))
for (i in 1:length(steps_files)){
  df <- read.csv(file=paste(steps_path, steps_files[i], sep=''))
  if(length(df$step) < 2){
    next
  }
  time_plot <- ggplot(df, aes(x=step, y=time, group=i)) +
  geom_line(linetype="dashed", color="blue", size=1.2)+
  geom_point(color="red", size=3) + 
  labs(title=steps_files[i]) +
	xlab("Steps") +
	ylab("Time (s)") 
  print(time_plot)
  size_plot <- ggplot(df, aes(x=step, y=size, group=i)) +
  geom_line(linetype="dashed", color="blue", size=1.2)+
  geom_point(color="red", size=3) + 
  labs(title=steps_files[i]) +
	xlab("Steps") +
	ylab(expression(paste("|",Delta[paste("E","'")],"|")))
  print(size_plot)  
}


```
</div>
<div class="clearer"></div>
