---
title: "Behavior Minimization tables"
author: "Mariano Cerrutti"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      results= "asis")
#install.packages("dplyr")
#install.packages("magrittr")
#install.packages("ggplot2")
#install.packages("jsonlite")
#install.packages("plot3D")
library(dplyr)
library(magrittr)
library(ggplot2)
library(jsonlite)
library(gridExtra)
library(grid)
library(lattice)
library(knitr)
library(scales)
library(plot3D)
library(stringr)
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
#creating general data frame
#file_dir <- '/home/mariano/code'
file_dir <- '/home/mariano/git_repo/henos'
experimental_composite <- read.csv(file=paste(file_dir, '/henos-automata/doc/experimental_setting/tmp_results/unrealizable_data_composite.csv',sep=''))
experimental_composite$name  <- str_replace_all(experimental_composite$name, "Scheduler", "Arbiter")
experimental_composite$name  <- str_replace_all(experimental_composite$name, "\\.\\(missing\\.assumption\\)", "\\.(missing\\.liveness)")
experimental_composite$name  <- str_replace_all(experimental_composite$name, "\\.missing\\.assumption", "\\.(missing\\.liveness)")
experimental_composite$name  <- str_replace_all(experimental_composite$name, "\\.removed\\.safety", "\\.(removed\\.safety)")
experimental_composite$name  <- str_replace_all(experimental_composite$name, "\\.", " ")
experimental_composite$liveness_count <- experimental_composite$assumptions_count + experimental_composite$guarantees_count
experimental_composite <- subset(experimental_composite, select = -c(realizable, ltl_model_build_time, model_build_time, composition_time,synthesis_time,alphabet_size,assumptions_count,guarantees_count,plant_states,plant_transitions,plant_controllable_transitions,plant_controllable_options,search_method))
#creating realizable data frame
realizable_data <- read.csv(file=paste(file_dir, '/henos-automata/doc/experimental_setting/tmp_results/realizable_data_composite.csv',sep=''))
realizable_data$name  <- str_replace_all(realizable_data$name, "\\.", " ")
experimental_composite$name  <- str_to_title(experimental_composite$name)
realizable_data$name  <- str_to_title(realizable_data$name)
realizable_data$name  <- str_replace_all(realizable_data$name, " Realizable", "")
realizable_data <- subset(realizable_data, select = -c(diagnosis_time,minimization_states,minimization_transitions,minimization_controllable_transitions,minimization_controllable_options,search_method,diagnosis_steps,realizable))
#merging data frames (realizable + liveness + safety)
realizable_data$liveness_count <- realizable_data$assumptions_count + realizable_data$guarantees_count
missing_assumptions <- subset(experimental_composite, grepl("Missing Liveness", name, fixed=TRUE))
missing_assumptions$name <- str_replace_all(missing_assumptions$name, " \\(Missing Liveness\\)", "")
missing_assumptions$diagnosis_time_liveness <- missing_assumptions$diagnosis_time
missing_assumptions$minimization_states_liveness <- missing_assumptions$minimization_states
missing_assumptions$minimization_transitions_liveness <- missing_assumptions$minimization_transitions
missing_assumptions$minimization_controllable_transitions_liveness <- missing_assumptions$minimization_controllable_transitions
missing_assumptions$minimization_controllable_options_liveness <- missing_assumptions$minimization_controllable_options
missing_assumptions$diagnosis_steps_liveness <- missing_assumptions$diagnosis_steps
missing_assumptions$liveness_count_liveness <- missing_assumptions$liveness_count
missing_assumptions <- subset(missing_assumptions, select = -c(diagnosis_time, minimization_states, minimization_transitions, minimization_controllable_transitions, minimization_controllable_options, diagnosis_steps, liveness_count))

removed_safety <- subset(experimental_composite, grepl("Removed Safety", name, fixed=TRUE))
removed_safety$name <- str_replace_all(removed_safety$name, " \\(Removed Safety\\)", "")
removed_safety$name <- str_replace_all(removed_safety$name, " \\(Missing Liveness\\)", "")
removed_safety$diagnosis_time_safety <- removed_safety$diagnosis_time
removed_safety$minimization_states_safety <- removed_safety$minimization_states
removed_safety$minimization_transitions_safety <- removed_safety$minimization_transitions
removed_safety$minimization_controllable_transitions_safety <- removed_safety$minimization_controllable_transitions
removed_safety$minimization_controllable_options_safety <- removed_safety$minimization_controllable_options
removed_safety$diagnosis_steps_safety <- removed_safety$diagnosis_steps
removed_safety$liveness_count_safety <- removed_safety$liveness_count
removed_safety <- subset(removed_safety, select = -c(diagnosis_time, minimization_states, minimization_transitions, minimization_controllable_transitions, minimization_controllable_options, diagnosis_steps,liveness_count))

compared_data <- merge(realizable_data, removed_safety, by.x ="name", by.y ="name", sort = FALSE)
compared_data <- merge(compared_data, missing_assumptions, by.x ="name", by.y ="name", sort = FALSE)

#compute general values
max_liveness_reduction <- max(compared_data$minimization_transitions_liveness / compared_data$plant_transitions)
max_safety_reduction <- max(compared_data$minimization_transitions_safety / compared_data$plant_transitions)
max_reduction <- max(c(max_liveness_reduction, max_safety_reduction))

min_liveness_reduction <- min(compared_data$minimization_transitions_liveness / compared_data$plant_transitions)
min_safety_reduction <- min(compared_data$minimization_transitions_safety / compared_data$plant_transitions)
min_reduction <- min(c(min_liveness_reduction, min_safety_reduction))

```
<style type="text/css">
.twoC {width: 100%}
.clearer {clear: both}
.twoC .table {max-width: 50%; float: right}
.twoC img {max-width: 50%; float: left}
table {
  margin: auto;
  border-top: 1px solid #666;
  border-bottom: 1px solid #666;
}
table thead th { border-bottom: 1px solid #ddd; }
th, td { padding: 5px; }
thead, tfoot, tr:nth-child(even) { background: #eee; }
pre{display:none;}
</style>

# Selected Graphs

## General Table

Specification sizes go from `r min(compared_data$plant_transitions)` transitions up to `r max(compared_data$plant_transitions)`.
Minimization reduction goes from `r max_reduction` up to `r min_reduction`.

## Reduction vs diagnosis time
```{r echo=FALSE}
#sive vs diagnosis time
general_data <- read.csv(file=paste(file_dir, '/henos-automata/doc/experimental_setting/tmp_results/unrealizable_data_composite.csv',sep=''))
c_coeff = general_data$minimization_controllable_transitions / general_data$plant_transitions	
m_coeff = general_data$minimization_transitions / general_data$plant_transitions	
kendall_reduction_time<-cor.test(general_data$diagnosis_time,1/m_coeff, method="kendall")
current_tau<- round(as.numeric(kendall_size_time$estimate[1]),5)
ggplot(general_data, aes(x=diagnosis_time, y=m_coeff)) +
	labs(title="Reduction vs diagnosis time") +
  xlab(bquote('Diagnosis time (s)' ( tau == .(current_tau) ))) + 
  ylab("Reduction") +  
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')



```

Kendall coefficient: `r kendall_reduction_time$estimate`

## Plant transitions size vs diagnosis time
```{r echo=FALSE}
#sive vs diagnosis time
kendall_size_time<-cor.test(general_data$diagnosis_time,general_data$plant_transitions, method="kendall")
current_tau<- round(as.numeric(kendall_size_time$estimate[1]),5)
ggplot(general_data, aes(x=diagnosis_time, y=plant_transitions)) +
	labs(title="Size vs diagnosis time") +
	xlab(bquote('Diagnosis time (s)' ( tau == .(current_tau) ))) +  
  ylab(expression(paste("|",Delta["E"],"|"))) +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +	
	geom_smooth(method='lm')

```

Kendall coefficient: `r kendall_size_time$estimate`

## Minimization and minimization controllability
```{r echo=FALSE}
#plant controllability vs minimization amount
no_robot_c_coeff = general_data$minimization_controllable_options / general_data$plant_states
no_robot_m_coeff = general_data$minimization_transitions / general_data$plant_transitions	
kendall_reduction_ctrl<-cor.test(no_robot_c_coeff,no_robot_m_coeff, method="kendall")
current_tau<- round(as.numeric(kendall_reduction_ctrl$estimate[1]),5)
ggplot(general_data, aes(x=no_robot_c_coeff, y=no_robot_m_coeff)) +
	labs(title='Minimization controllability vs minimization amount ') +
	xlab(bquote('Minimization controllability' ( tau == .(current_tau) ))) +
	ylab("Reduction") +
	scale_y_log10() +
	scale_x_log10() +	
	geom_point(color='red') +
	geom_smooth(method='lm')	



```

Kendall coefficient: `r kendall_reduction_ctrl$estimate`

## Compared times between synthesis and diagnosis

```{r echo=FALSE}
#dividing compared data by case
cases <- c("Genbuf", "Ahb", "Collector", "Lift", "Exploration","Cat","Airport","Bidding","Transfer","Travel")

cases_names <- c("Genbuf", "Ahb", "Collector", "Lift Controller", "Exploration Robot","Cat and Mouse","Airport Tower","Bidding Workflow","Transfer Line","Travel Agency" )
for (i in 1:length(cases)){
  current_data <- subset(compared_data, grepl(cases[i], name))  
  print(ggplot(current_data, aes(x=synthesis_time, y=diagnosis_time_liveness)) +
  	labs(title=paste("Synthesis vs diagnosis time (liveness)", cases_names[i])) +
  	xlab(expression(paste("Synthesis time (s)"))) +
    ylab("Diagnosis time liveness (s)") +
  	scale_y_log10() +
    scale_x_log10() +	
  	geom_point(color='red') +	
  	geom_smooth(method='lm'))
  
  print(ggplot(current_data, aes(x=synthesis_time, y=diagnosis_time_safety)) +
  	labs(title=paste("Synthesis vs diagnosis time (safety)", cases_names[i])) +
  	xlab(expression(paste("Synthesis time (s)"))) +
    ylab("Diagnosis time safety (s)") +
  	scale_y_log10() +
    scale_x_log10() +	
  	geom_point(color='red') +	
  	geom_smooth(method='lm'))
  
}


#kable(times_table, caption = "Times table", col.names=c("Specification","Diagnosis(s)","Liveness fluents", "Plant transitions", "Min. transitions","Minimization pct.(%)","Min. steps"))

```

## Compared time against time and formula size

```{r echo=FALSE}
compared_data_no_zero <- compared_data[compared_data$plant_transitions > 0,]
x <- compared_data_no_zero$liveness_count_liveness
y <- log(compared_data_no_zero$plant_transitions)
z <- log(compared_data_no_zero$diagnosis_time_liveness)
# Compute the linear regression 
fit <- lm(z ~ x + y)
# create a grid from the x and y values (min to max) and predict values for every point
# this will become the regression plane
grid.lines = 20
x.pred <- seq(min(x), max(x), length.out = grid.lines)
y.pred <- seq(min(y), max(y), length.out = grid.lines)
xy <- expand.grid( x = x.pred, y = y.pred)
z.pred <- matrix(predict(fit, newdata = xy), 
                 nrow = grid.lines, ncol = grid.lines)
# create the fitted points for droplines to the surface
fitpoints <- predict(fit)
# scatter plot with regression plane
scatter3D(x, y, z, pch = 19, cex = 1,colvar = NULL, col="red", theta = -70, phi = 0, bty="b",
          xlab = "|A|+|G|", ylab = "log|Delta|", zlab = "log(Diagnosis (s))", surf = list(x = x.pred, y = y.pred, z = z.pred,  
                      facets = FALSE, fit = fitpoints, col=ramp.col (col = c("dodgerblue3","seagreen2"), n = 300, alpha=0.5), border="blue"), main = "Diagnosis time vs size and formula size(liveness)")

scatter3D(x, y, z, pch = 19, cex = 1,colvar = NULL, col="red", theta = 70, phi = 0, bty="b",
          xlab = "|A|+|G|", ylab = "log|Delta|", zlab = "log(Diagnosis) (s)", surf = list(x = x.pred, y = y.pred, z = z.pred,  
                      facets = FALSE, fit = fitpoints, col=ramp.col (col = c("dodgerblue3","seagreen2"), n = 300, alpha=0.5), border="blue"), main = "Diagnosis time vs size and formula size(liveness, rotated)")

x <- compared_data_no_zero$liveness_count_safety
y <- log(compared_data_no_zero$plant_transitions)
z <- log(compared_data_no_zero$diagnosis_time_safety)
# Compute the linear regression 
fit <- lm(z ~ x + y)
# create a grid from the x and y values (min to max) and predict values for every point
# this will become the regression plane
grid.lines = 20
x.pred <- seq(min(x), max(x), length.out = grid.lines)
y.pred <- seq(min(y), max(y), length.out = grid.lines)
xy <- expand.grid( x = x.pred, y = y.pred)
z.pred <- matrix(predict(fit, newdata = xy), 
                 nrow = grid.lines, ncol = grid.lines)
# create the fitted points for droplines to the surface
fitpoints <- predict(fit)
# scatter plot with regression plane
scatter3D(x, y, z, pch = 19, cex = 1,colvar = NULL, col="red", theta = -70, phi = 0, bty="b",
          xlab = "|A|+|G|", ylab = "log|Delta|", zlab = "log(Diagnosis (s))", surf = list(x = x.pred, y = y.pred, z = z.pred,  
                      facets = FALSE, fit = fitpoints, col=ramp.col (col = c("dodgerblue3","seagreen2"), n = 300, alpha=0.5), border="blue"), main = "Diagnosis time vs size and formula size(safety)")

scatter3D(x, y, z, pch = 19, cex = 1,colvar = NULL, col="red", theta = 70, phi = 0, bty="b",
          xlab = "|A|+|G|", ylab = "log|Delta|", zlab = "log(Diagnosis) (s)", surf = list(x = x.pred, y = y.pred, z = z.pred,  
                      facets = FALSE, fit = fitpoints, col=ramp.col (col = c("dodgerblue3","seagreen2"), n = 300, alpha=0.5), border="blue"), main = "Diagnosis time vs size and formula size(safety)")

```
</div>
<div class="clearer"></div>
